### 2017-12-18 paper/paper.tex
added template for paper and brief potential outline

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
\documentclass{llncs}
%
\usepackage{makeidx}  % allows for indexgeneration
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tikz}

%
\begin{document}
%
\mainmatter              % start of the contributions
%
\title{An Executable Formal Semantics For A Functional Actor Language}
%
\author{Xiaohong Chen, Lucas Pe\~{n}a}
%
\institute{University of Illinois at Urbana-Champaign, \\
\email{\{xc3, lpena7\}@illinios.edu}}

\maketitle              % typeset the title of the contribution

\begin{abstract}
A simple reference actor language has been proposed in~\cite{}, serving as a sound mathematical calculus foundation for various actor languages used in distributed applications that involves concurrency. Even though the authors of~\cite{} provided in the paper an operational semantics of the actor language, an executable implementation was not given. In this project, we will give the reference actor language an implementation that by construction conforms to its formal operational semantics using the K framework~\cite{}, a rule-based semantic framework. We will show that our executable formal semantics are capable of executing some meaningful actor systems examples. We hope our executable formal semantics can be served as a starting point for future work in developing automatic equivalence provers using K framework.
\end{abstract}
%
\section{Introduction}
\subsection{Related Work}

\section{The Actor Language in K}
\subsection{Configuration}
\subsection{Syntax and Evaluation Contexts}
\subsection{Semantics}
\subsection{In-depth Example}

\section{Conclusion and Future Work}

%
% ---- Bibliography ----
%
\bibliographystyle{ieeetr}

\bibliography{references}

\end{document}

### 2017-12-19 paper/paper.tex
very rough intro/related work

@@
 \begin{abstract}
-A simple reference actor language has been proposed in~\cite{}, serving as a sound mathematical calculus foundation for various actor languages used in distributed applications that involves concurrency.
-Even though the authors of~\cite{} provided in the paper an operational semantics of the actor language, an executable implementation was not given.
-In this project, we will give the reference actor language an implementation that by construction conforms to its formal operational semantics using the K framework~\cite{}, a rule-based semantic framework.
-We will show that our executable formal semantics are capable of executing some meaningful actor systems examples.
-We hope our executable formal semantics can be served as a starting point for future work in developing automatic equivalence provers using K framework.
+A simple reference actor language has been proposed in~\cite{}, serving as a
+sound mathematical calculus foundation for various actor languages used in
+distributed applications that involves concurrency. Even though the authors
+of~\cite{} provided in the paper an operational semantics of the actor language,
+an executable implementation was not given. In this project, we will give the
+reference actor language an implementation that by construction conforms to its
+formal operational semantics using the K framework~\cite{}, a rule-based
+semantic framework. We will show that our executable formal semantics are
+capable of executing some meaningful actor systems examples. We hope our
+executable formal semantics can be served as a starting point for future work in
+developing automatic equivalence provers using the K framework.
 \end{abstract}
@@
 \section{Introduction}
+The K framework~\cite{} is a framework for defining executable operational
+semantics of a programming language. K is based on rewriting logic, organizing
+the state of a program into cells and rewriting the particular parts of the
+configuration. K also has access the entire computation at any particular
+time. These features and more allow for difficult language constructs to be
+designed with ease in K. On top of that, K provides backend tooling for
+additional features based on the semantics of a programming language, such as a
+semantic debugger and a full formal verifier. See Figure~\ref{fig:k-tools} for a
+complete view of the tools one gets from K based off an operational semantics.
+
 \subsection{Related Work}
+
+\begin{figure}
+          \centering
+          \includegraphics[scale=0.13]{../k-overview.png}
+	  \caption{Backend tools K provides from just an operational
+            semantics. Some tools such as a semantics-based compiler and
+            test-case generation are in progress.}
+          \label{fig:k-tools}
+\end{figure}
+To demonstrate the power of K, languages as complex as C, Java, and JavaScript
+have been fully defined using the K framework~\cite{ , , }. On top of that, in
+all of these languages and more, nontrivial programs have been formally verified
+using K's prover, such as proofs involving AVL trees and red-black trees. We
+would like to add an actor-based language to the growing list of languages
+defined in K, so we can take advantage of K's formal verification engine and
+more.
+
+Semantics of actor-based languages have been defined on paper, for example
+in~\cite{}. Additionally, there are many implementations of actor-based systems,
+including Erlang~\cite{}, Akka~\cite{}, Scheme~\cite{}, and much more. However,
+there is currently no formally defined \textit{executable} operational semantics
+of an actor-based language. In K, there was previous work done to define the
+semantics of Orc, a concurrent programming language~\cite{}, though that work is
+incomplete.
+
+In this paper, we aim to define the semantics of the actor language proposed
+in~\cite{}.  We choose this language as the semantics are clearly defined in the
+paper, and it is one of the more simple actor frameworks. Defining this language
+in K will give assurance to the correctness of the language - as K is executable
+this can be tested much easier than defining a language on paper. It will also
+provide more assurance on K's language-defining ability, as well as open up to
+formal analysis using the tools seen in Figure~\ref{fig:k-tools}.
 

### 2017-12-19 paper/paper.tex
syntax and reduction contexts

@@
 \section{The Actor Language in K}
+
 \subsection{Configuration}
-\subsection{Syntax and Evaluation Contexts}
+
+\subsection{Syntax and Reduction Contexts}
+Syntax for constructs in K is specified using BNF notation. For example, we
+specify values (where reduction can no longer happen) as
+\begin{verbatim}
+  syntax Val  ::= CVal                                    
+                | "lambda" "(" Id "," Exp ")" [binder]
+                | "pr" "(" Val "," Val ")"
+\end{verbatim}
+where \texttt{CVal} represents the communicable values, \texttt{lambda}
+represents lambda expressions, and \texttt{pr} represents pairs of values.  The
+\texttt{binder} attribute is used in K's backend for substitution, as it
+specifies that \texttt{Id} is bound in the term \texttt{Exp}.
+
+In K, we can also use syntax to express contexts in which reduction is allowed.
+In the actor language, reduction contexts are separately defined to specify
+evaluation order of expressions. For example, the set of reduction contexts for
+functions in the actor language are specified as
+\[ \mathbb{F}_{n+m+1}(\mathbb{V}^n,\mathbb{R},\mathbb{E}^m) \]
+This states that the argument of a function can be evaluated only when the first
+$n$ arguments have already been evaluated. In K, this is simply specified using
+the attribute \texttt{seqstrict} which states the arguments of a syntactic
+construct are evaluated in order. Addition, for example, is specified in K as
+\begin{verbatim}
+syntax Exp ::= "add" "(" Exp "," Exp ")" [seqstrict]
+\end{verbatim}
+Note nothing beyond the appropriate strictness attribute is needed to specify
+reduction contexts in K for this language.
+
+For the branching, we would like to only specify that only the first argument
+should reduce to a value, to avoid reduction in the branch we end up not taking.
+In the actor semantics from~\cite{}, this is accomplished with the following:
+\[ \texttt{if}(e_0, e_1, e_2) \;\;\;\text{abbreviates}\;\;\; \texttt{app}(\texttt{br}(e_0, \lambda z.e_1, \lambda z.e_2), \texttt{nil}) \;\;\;\text{for $z$ fresh} \]
+Notice that the second and third arguments in the branch construct are lambda
+expressions, which are values, and thus will not be reduced any farther. In our
+K semantics, we emulate this, but we could also define \texttt{br} directly to
+be only strict in the first argument as follows:
+\begin{verbatim}
+syntax Exp ::= "br" "(" Exp "," Exp "," Exp ")" [strict(1)]
+\end{verbatim}
+Strictness constructs like this avoid unnecessary syntactic sugar, and cleanly
+specify most reduction contexts one would require.
+
 \subsection{Semantics}
+
 \subsection{In-depth Example}

### 2017-12-19 paper/paper.tex
modified intro, moved related work to own section, wrote configuration section

@@
 
-\subsection{Related Work}
+In the rest of the paper we discuss related work, then the actor semantics in
+some detail, including the configuration, the syntax and how we handle reduction
+contexts in K, the semantics, and an in-depth example. We then conclude and
+discuss future work.
+
+\section{Related Work}
 
@@
 To demonstrate the power of K, languages as complex as C, Java, and JavaScript
-have been fully defined using the K framework~\cite{ , , }. On top of that, in
+have been fully defined using the K framework~\cite{c,java,jscript}. On top of that, in
 all of these languages and more, nontrivial programs have been formally verified
@@
 \section{The Actor Language in K}
+In this section, we describe in detail some important features of the actor
+language from~\cite{}. We cover some important features from K and how they were
+used to define key concepts of the actor language.
 
 \subsection{Configuration}
+All languages in K use a configuration to specify the current state of a
+program. For simple languages like the lambda calculus or a simple \texttt{IMP}
+language, there may only be one cell to hold the current computation (the
+\texttt{k} cell) and perhaps another \texttt{env} cell for the current
+environment. For the actor language, we have the following configuration:
+\begin{verbatim}
+configuration 
+  <T>
+    <actors>
+      <actor multiplicity="*">     // a multiset of actors
+        <k> exec($PGM:Exp) </k>    // actor state
+        <id> initactor </id>       // actor id
+      </actor>
+    </actors>
+    <messages>
+      <message  multiplicity="*">  // a multiset of messages
+        .K
+      </message>
+    </messages>
+    <definedaddr>                  // list of defined actors'
+      ListItem(initactor)          // addresses
+    </definedaddr>
+  </T>
+\end{verbatim}
+In addition to defining the state of a program, the configuration is also used
+to define the initial state of a program. Initially, we only have one actor,
+with the unique identifier \texttt{initactor}. It also contains the program in
+the \texttt{exec} state ready to be executed. The variable \texttt{\$PGM} comes
+from an external file. The notation \texttt{multiplicity=*} is used to specify
+that there can be any number of \texttt{actor} cells and \texttt{message} cells
+as a multiset of actors and messages respectively. Initially there are no
+messages, represented using K's builtin \texttt{.K}. Finally, the
+\texttt{definedaddr} cell is used to keep track of addresses of defined
+actors. We need to keep track of this for the side condition of some semantic
+rules (see Section~\ref{sec:semantics}).
+
+For our K definition, we only define a single actor system, so there are no
+external actors or receptionists. To add these one can simply add these as
+additional cells in the configuration, initialized to the empty list.
 
@@
 
-\subsection{Semantics}
+\subsection{Semantics}\label{sec:semantics}
 

### 2017-12-20 paper/paper.tex
nothing
add sec 2.3 & 2.4

@@
 In this section, we describe in detail some important features of the actor
-language from~\cite{}. We cover some important features from K and how they were
+language from~\cite{actor}. We cover some important features from K and how 
+they were
 used to define key concepts of the actor language.
@@
 \subsection{Semantics}\label{sec:semantics}
+Semantics in K is given as \emph{rewriting rules} of the form $l \Rightarrow r$.
+For example, the  beta-reduction rule (beta-v) is specified as
+\begin{verbatim}
+  rule app(lambda(X:Id, E:Exp), V:Val) => E [ V / X ]
+\end{verbatim}
+where \texttt{E [ V / X ]} is the result of substituting \texttt{V} for 
+\texttt{X} in \texttt{E} using K's internal substitution mechanism.
+Conditional reduction rules can also be easily specified.
+For example, the branching rule (br) is specified as two K rules
+\begin{verbatim}
+  rule br(nil, V1:Val, V2:Val) => V2
+  rule <k> br(V:Val, V1:Val, V2:Val) => V1 ... </k>
+       <definedaddr> X </definedaddr>
+    requires notBool((isId(V) andBool notBool(V in X)) orBool V ==K nil)
+\end{verbatim}
+The first rule says if the first argument is \texttt{nil}, the branching 
+operator \texttt{br} returns its third argument.
+The second rule is a bit complicated.
+It says if the first argument is neither \texttt{nil} nor 
+unknown addresses, the branching operator \texttt{br} returns its second 
+argument.
+
+The single-step transition relation $\mapsto$ on actor configurations is 
+similarly specified using K rules.
+For example, the \texttt{<init: a, a1>} transition rule is specified as
+\begin{verbatim}
+  rule <actor>
+         <k> initbeh(A1, V:Val) => nil ... </k>
+         <id> A </id>
+       </actor>
+       <actor>
+         <k> uninit(A) => ready(V) ... </k>
+         <id> A1 </id>
+       </actor>
+\end{verbatim}
+The rule involves two actors as there are two actor cells 
+\texttt{<actor>}\ \dots\ \texttt{</actor>} in the rule.
+The first actor is the \emph{initializer} actor while the second is the actor 
+\emph{being initialized}.
+K supports to only specify components that are relevant to the rule. This is 
+known as the \emph{framing principle}.
+The initializer actor executes \texttt{initbeh(A1, V:Val)} and gets value 
+\texttt{nil}, as specified in the rule.
+The rest computation or \emph{the reduction context} is unchanged and kept in 
+the following~``\texttt{...}''.
+
+Reduction context can be mentioned explicitly when needed.
+For example in the following \texttt{<bec: a, a1>} rule,
+\begin{verbatim}
+  rule <actor>
+         <k> (become(V:Val) ~> RestComputation) => ready(V) </k>
+         ...
+       </actor>
+       (.Bag => <actor>
+                  <k> nil ~> RestComputation </k>
+                  <id> !A1:Id </id>
+                </actor>)
+       <definedaddr> Ads => Ads ListItem(!A1) </definedaddr>
+\end{verbatim}
+the reduction context \texttt{RestComputation} is explicitly passed to a 
+newly-generated actor.
+The tilde arrow expression \verb|T ~> R| 
+means the decomposition \verb|R[T]| with reduction context \texttt{R} and redex 
+\texttt{T}.
 
 \subsection{In-depth Example}
+We test our actor semantics on an example of tree recursion~\cite{actor}.
+The problem is to calculate the product of all leaves of a binary tree.
+The problem is solved by a divide-and-conquer algorithm which calculates the 
+results for two subtrees and multiplies the results.
+The algorithm is implemented using a \emph{join continuation} as follows.
+\begin{verbatim}
+let(bind(sink,
+  rec(lambda(b, lambda(m, become(b))))),
+let(bind(ident,
+  lambda(m, m)),
+let(bind(joincont,
+  rec(lambda(b, lambda(c, lambda(nargs, lambda(firstnum, lambda(num,
+    if(eq?(nargs, 0),
+       become(app(app(app(b, c), 1), num)),
+       seq(become(sink),
+           send(c, mult(firstnum, num))))))))))),
+let(bind(treeprod,
+  rec(lambda(b, lambda(self, lambda(m,
+    seq(become(app(b, self)),
+        if(isnat(tree(m)),
+           send(cust(m), tree(m)),
+           letactor(bind(newcust, app(app(app(joincont, cust(m)), 0), nil)),
+             seq(send(self, pr(left(tree(m)), newcust)),
+                 send(self, pr(right(tree(m)), newcust))))))))))),
+let(bind(tr, 
+  pr(pr(1, pr(2, pr(3, 4))), pr(pr(5, 6), 7))),
+letactor(
+  bind(tpactor, app(treeprod, tpactor)),
+  bind(custactor, ident),
+  send(tpactor, pr(tr, custactor))))))))
+\end{verbatim}
+Remind that our semantics initializes the initial actor with the behavior of 
+executing the above lambda expression.
+Therefore after five \texttt{let}-expressions, the initial actor creates two 
+actors. One is the \texttt{tpactor} that calculates the tree product.
+The other is the \texttt{custactor} that receives the result.
+The initial actor sends \texttt{tpactor} a message containing a binary tree 
+whose leaves are $1, 2, \dots, 7$, and the address of the customer actor 
+\texttt{custactor}.
+When the actor system terminates, we get the following configuration
+\begin{verbatim}
+<T>
+  <actors>
+    <actor>
+      <k> ready ( ... ) </k>
+      <id> _93 </id>
+    </actor>
+    <actor>
+      <k> ready ( ... ) </k>
+      <id> _179 </id>
+    </actor>
+    .... ....
+    <actor>
+      <k> ready ( ... ) </k>
+      <id> _45 </id>
+    </actor>
+    <actor>
+      <k> exec ( nil ) </k>
+      <id> initactor </id>
+    </actor>
+    <actor>
+      <k> exec ( 5040 ) </k>
+      <id> _46 </id>
+    </actor>
+    ......
+    ......
+  </actors>
+  <messages> .MessageCellBag </messages>
+  <definedaddr> ... </definedaddr>
+</T>
+\end{verbatim}
+In the configuration there are many idle actors generated during the 
+computation. The customer actor, which in this execution has identity 
+\texttt{\_46}, is holding the final product of 5040.
 

### 2017-12-20 paper/paper.tex
wip on conclusion

@@
 
+In this paper we showed how to define the actor semantics from~\cite{} using the
+K framework. We described in detail the syntax and semantics of the language in
+K, as well as the configuration for our actor language. We also showed how we
+can use K's strictness attributes to emulate the reduction contexts described
+in~\cite{}. Finally, we discussed a complicated actor program, the tree product
+example, and its encoding in K.
+
+One immediate area for future work includes defining more actor programs and
+more in-depth actor programs in K. Having a large test suite of complicated
+examples can be used to ensure that the semantics in K and the semantics
+from~\cite{} do not have any bugs. It can also be used to determine rule
+coverage, affirming that all semantic rules can be applied.
+
+Another area for future work inovlves extending
+
+Finally, an important area for future work involves taking advantage of K's
+backend tools for formal analysis, such as proving actor programs correct using
+K's verification engine. For verification, K uses reachability logic~\cite{}, a
+language-independent formal verification framework. Reachability logic supports
+all-path reachability, so it can be used to verify programs involving concurrent
+semantics. However, in order to fully take advantage of this verification, one
+would need to implement partial-order reduction in K in order to reduce the
+state space.
+
 %

### 2017-12-20 paper/paper.tex
small edits, mostly spacing for 2.3, 2.4

@@
 including Erlang~\cite{}, Akka~\cite{}, Scheme~\cite{}, and much more. However,
-there is currently no formally defined \textit{executable} operational semantics
+there is currently no formally defined \emph{executable} operational semantics
 of an actor-based language. In K, there was previous work done to define the
@@
        <definedaddr> X </definedaddr>
-    requires notBool((isId(V) andBool notBool(V in X)) orBool V ==K nil)
+    requires notBool((isId(V) andBool notBool(V in X))
+                              orBool V ==K nil)
 \end{verbatim}
@@
 \subsection{In-depth Example}
-We test our actor semantics on an example of tree recursion~\cite{actor}.
-The problem is to calculate the product of all leaves of a binary tree.
-The problem is solved by a divide-and-conquer algorithm which calculates the 
-results for two subtrees and multiplies the results.
-The algorithm is implemented using a \emph{join continuation} as follows.
+We test our actor semantics on many examples. One of the more complicated test
+cases is an example of tree recursion~\cite{actor}.  The problem is to calculate
+the product of all leaves of a binary tree.  The problem is solved by a
+divide-and-conquer algorithm which calculates the results for two subtrees and
+multiplies the results.  The algorithm is implemented using a
+\emph{join continuation} as follows.
+\small
 \begin{verbatim}
@@
 \end{verbatim}
-Remind that our semantics initializes the initial actor with the behavior of 
+\normalsize
+Recall that our semantics initializes the initial actor with the behavior of
 executing the above lambda expression.

### 2017-12-20 paper/paper.tex
conclusion section

@@
 
-\subsection{Configuration}
+\subsection{Configuration}\label{sec:configuration}
 All languages in K use a configuration to specify the current state of a
@@
 language, there may only be one cell to hold the current computation (the
-\texttt{k} cell) and perhaps another \texttt{env} cell for the current
-environment. For the actor language, we have the following configuration:
+\texttt{<k>}\ \dots\ \texttt{</k>} cell) which is required for all languages
+defined in K. For the actor language, we have the following configuration:
 \begin{verbatim}
@@
 
-Another area for future work inovlves extending
-
-Finally, an important area for future work involves taking advantage of K's
+Another important area for future work involves taking advantage of K's
 backend tools for formal analysis, such as proving actor programs correct using
@@
 state space.
+
+Finally, we would also like to extend our semantics to allow interaction between
+actor systems by adding external actors and receptionists, as mentioned in
+Section~\ref{sec:configuration}. This would allow us to define more complicated
+programs, and it would also allow us to define programs like the tree product
+program more compactly. Additionally, it would allow us to begin asking
+questions regarding observational equivalence of actor systems, and perhaps even
+take advantage of K's analysis tools to prove such equivalences.
 

### 2017-12-20 paper/paper.tex
added all citations

@@
 \begin{abstract}
-A simple reference actor language has been proposed in~\cite{}, serving as a
+A simple reference actor language has been proposed in~\cite{actor}, serving as a
 sound mathematical calculus foundation for various actor languages used in
 distributed applications that involves concurrency. Even though the authors
-of~\cite{} provided in the paper an operational semantics of the actor language,
+of~\cite{actor} provided in the paper an operational semantics of the actor language,
 an executable implementation was not given. In this project, we will give the
 reference actor language an implementation that by construction conforms to its
-formal operational semantics using the K framework~\cite{}, a rule-based
+formal operational semantics using the K framework~\cite{kframework}, a rule-based
 semantic framework. We will show that our executable formal semantics are
@@
 \section{Introduction}
-The K framework~\cite{} is a framework for defining executable operational
+The K framework~\cite{kframework} is a framework for defining executable operational
 semantics of a programming language. K is based on rewriting logic, organizing
@@
 To demonstrate the power of K, languages as complex as C, Java, and JavaScript
-have been fully defined using the K framework~\cite{c,java,jscript}. On top of that, in
+have been fully defined using the K framework~\cite{kc,kjava,kjs}. On top of that, in
 all of these languages and more, nontrivial programs have been formally verified
@@
 Semantics of actor-based languages have been defined on paper, for example
-in~\cite{}. Additionally, there are many implementations of actor-based systems,
-including Erlang~\cite{}, Akka~\cite{}, Scheme~\cite{}, and much more. However,
+in~\cite{actor}. Additionally, there are many implementations of actor-based systems,
+including Erlang~\cite{erlang}, Akka~\cite{akka}, Scheme~\cite{scheme}, and much more. However,
 there is currently no formally defined \emph{executable} operational semantics
 of an actor-based language. In K, there was previous work done to define the
-semantics of Orc, a concurrent programming language~\cite{}, though that work is
+semantics of Orc, a concurrent programming language~\cite{orc}, though that work is
 incomplete.
@@
 In this paper, we aim to define the semantics of the actor language proposed
-in~\cite{}.  We choose this language as the semantics are clearly defined in the
+in~\cite{actor}.  We choose this language as the semantics are clearly defined in the
 paper, and it is one of the more simple actor frameworks. Defining this language
@@
 should reduce to a value, to avoid reduction in the branch we end up not taking.
-In the actor semantics from~\cite{}, this is accomplished with the following:
+In the actor semantics from~\cite{actor}, this is accomplished with the following:
 \[ \texttt{if}(e_0, e_1, e_2) \;\;\;\text{abbreviates}\;\;\; \texttt{app}(\texttt{br}(e_0, \lambda z.e_1, \lambda z.e_2), \texttt{nil}) \;\;\;\text{for $z$ fresh} \]
@@
 
-In this paper we showed how to define the actor semantics from~\cite{} using the
+In this paper we showed how to define the actor semantics from~\cite{actor} using the
 K framework. We described in detail the syntax and semantics of the language in
@@
 can use K's strictness attributes to emulate the reduction contexts described
-in~\cite{}. Finally, we discussed a complicated actor program, the tree product
+in~\cite{actor}. Finally, we discussed a complicated actor program, the tree product
 example, and its encoding in K.
@@
 examples can be used to ensure that the semantics in K and the semantics
-from~\cite{} do not have any bugs. It can also be used to determine rule
+from~\cite{actor} do not have any bugs. It can also be used to determine rule
 coverage, affirming that all semantic rules can be applied.
@@
 backend tools for formal analysis, such as proving actor programs correct using
-K's verification engine. For verification, K uses reachability logic~\cite{}, a
+K's verification engine. For verification, K uses reachability logic~\cite{reachabilitylogic}, a
 language-independent formal verification framework. Reachability logic supports

### 2017-12-20 paper/paper.tex
minor

@@
 \institute{University of Illinois at Urbana-Champaign, \\
-\email{\{xc3, lpena7\}@illinios.edu}}
+\email{\{xc3,lpena7\}@illinios.edu}}
 
@@
   \centering
-          \includegraphics[scale=0.13]{../k-overview.png}
+  \includegraphics[width=0.8\textwidth]{../k-overview.png}
   \caption{Backend tools K provides from just an operational
@@
 \texttt{X} in \texttt{E} using K's internal substitution mechanism.
+K rules start with the keyword \texttt{rule}. The left hand side of the rule 
+and right hand side of the rule are separated by a double arrow~``\texttt{=>}''.
+
 Conditional reduction rules can also be easily specified.
@@
 argument.
+The \texttt{requires} keyword is used to specify rewriting conditions that 
+decide when a rewrite rule can be applied.
 
@@
 For example, the \texttt{<init: a, a1>} transition rule is specified as
+\small
 \begin{verbatim}
@@
 \end{verbatim}
+\normalsize
 The rule involves two actors as there are two actor cells 
@@
 \texttt{nil}, as specified in the rule.
-The rest computation or \emph{the reduction context} is unchanged and kept in 
+The rest computation or so-called \emph{reduction context} is unchanged and 
+kept in 
 the following~``\texttt{...}''.
@@
 Reduction context can be mentioned explicitly when needed.
-For example in the following \texttt{<bec: a, a1>} rule,
+For example, in the following \texttt{<bec: a, a1>} rule,
+\small
 \begin{verbatim}
@@
 \end{verbatim}
+\normalsize
 the reduction context \texttt{RestComputation} is explicitly passed to a 
-newly-generated actor.
+newly-generated actor with a fresh identity \verb|!A1|.
 The tilde arrow expression \verb|T ~> R| 
@@
 \normalsize
+
 Recall that our semantics initializes the initial actor with the behavior of 
 executing the above lambda expression.
-Therefore after five \texttt{let}-expressions, the initial actor creates two 
+Therefore after five nested \texttt{let}-expressions, the initial actor creates 
+two 
 actors. One is the \texttt{tpactor} that calculates the tree product.
@@
 When the actor system terminates, we get the following configuration
+\small
 \begin{verbatim}
@@
 \end{verbatim}
+\normalsize
 In the configuration there are many idle actors generated during the 
@@
 \section{Conclusion and Future Work}
-
+\label{sec:conclusion}
 In this paper we showed how to define the actor semantics from~\cite{actor} using the

### 2017-12-21 test/test_all.sh
changed name of output files, added test_all.sh to test all files

@@ -1,0 +1,39 @@
+#!/usr/bin/env bash
+COUNT=1
+NUM_ERRORS=0
+
+function begin_case () {
+  printf "\e[94m%-2s\e[0m %-1s Running \e[1m%-30s\e[0m ...\n" "$COUNT" "|" $1
+}
+
+function report_case () {
+  if [ $1 == 0 ]
+  then printf "\e[F\e[45G\e[32m%-30s\e[0m\n" "SUCCESS"
+  else
+       printf "\e[45G\e[31m%-30s\e[0m\n" "FAILURE";
+    (( NUM_ERRORS += 1 ));
+  fi
+}
+
+function final_report () {
+  if [ $NUM_ERRORS == 0 ]
+  then (printf "    \e[1m\e[32m$(( COUNT-1 )) programs have been successfully run.\e[0m\n"; exit 0)
+  else (printf "    \e[1m\e[31m$NUM_ERRORS out of $(( COUNT-1 )) programs did not match the expected output.\e[0m\n"; exit 1)
+  fi
+}
+
+for file in `ls *.actor`;
+  do
+    begin_case $file
+    krun -d ../src $file > temp.xml
+    xmllint --format temp.xml | tail -n +2 | diff $file.out - > /dev/null;
+    rm temp.xml
+    if [ $? != 0 ]
+      then report_case 1 $file
+      else report_case 0 $file
+    fi;
+    (( COUNT+=1 ));
+done;
+printf -- "---------------------------------------------------\n"
+
+final_report

### 2017-12-21 paper/paper.tex

@@
 The second rule is a bit complicated.
-It says if the first argument is neither \texttt{nil} nor 
-unknown addresses, the branching operator \texttt{br} returns its second 
+It says if the first argument is neither \texttt{nil} nor an
+unknown address, the branching operator \texttt{br} returns its second
 argument.
@@
 \texttt{nil}, as specified in the rule.
-The rest computation or so-called \emph{reduction context} is unchanged and 
+The rest of the computation or so-called \emph{reduction context} is unchanged and
 kept in 
@@
 
-Reduction context can be mentioned explicitly when needed.
+Reduction contexts can be mentioned explicitly when needed.
 For example, in the following \texttt{<bec: a, a1>} rule,
